Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-03-09 supCLT.tex
supCLT.tex: 0309 submitted version to EJP and arXiv

%%----Versions-----------------------------
%supCLT-8.tex 2019/03/08 by Zhenyao
%supCLT-7.tex 2019/03/08 by Renming
%supCLT-6.tex 2019/03/07 by Zhenyao
%supCLT-5.tex 2019/03/07 by Jianjie
%supCLT-4.tex 2019/03/07 by Yanxia
%supCLT-3.tex 2019/03/06 by Jianjie
%supCLT-2.tex 2019/03/05 by Renming
%supCLT.tex 2019/03/04 by Zhenyao
% supclt0220.tex 2019/02/20 by Jianjie
% supclt0217.tex 2019/02/14 by Renming
% supclt0214.tex 2019/02/14 by Yanxia
% supclt0211.tex 2019/02/11 by Zhenyao
% supCLT0128.tex 2019/01/28 by Renming
% supCLT0127.tex 2019/01/27 by Yanxia
% supCLT0124.tex 2019/01/24 by Jianjie
% supCLT0114.tex 2019/01/14 by Yanxia
% supCLT0107.tex 2019/01/07 by Jianjie
% supclt1231.tex 2018/12/14 by Zhenyao
% supclt1213.tex 2018/12/14 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie

@@

    \\ University of Illinois of Illinois at Urbana-Champaign

@@

Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$.
Let $\psi$ be a branching mechanism which is close to a function of the form
$\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. In this paper, we study asymptotic behaviors of
$(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$.
    For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$.
    Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
    the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.

@@

\subsubsection{Critical branching rate regime}
    For each $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
\begin{equation}\label{tilde-m}
    \widetilde{m}[f]
        := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
\end{equation}
%ZS: here and below, I changed all \wide to \widetilde without %
    According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
   We will prove in Lemma \ref{prop: alpha stable rv} that
   $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
\begin{thm}
\label{thm: critical clt}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$,
    under $\mathbb{P}_{\mu}(\cdot|D^c)$,
    it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
        \xrightarrow[t\to \infty]{d} \widetilde{\zeta},
\]
    where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
    characteristic function
\[
     \mathbf E [e^{i\theta \widetilde{\zeta}}]
    =\exp(\widetilde{m}[\theta f]),
    \quad \theta\in \mathbb R.
\]
\end{thm}

@@

\begin{proof}
    Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the Lemma \ref{lem: temp}.
    For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
\begin{align}
    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda
    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda
    \\& \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda
    \\&\leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
\end{align}
    Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
\begin{align}
    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
\end{align}
    Note that
\begin{align}
    &(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b)
    \\&\leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
\end{align}
    So the desired result is true with
\[
    C
    := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
    \qedhere
\]
\end{proof}
    For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write
\[
    %\|Y\|_{\mathbb P;p}:= E[|Y|^p]^{1/p}.
    \|Y\|_{\mathbb P;p}:= \mathbb P[|Y|^p]^{1/p}.
\]
\begin{lem}
\label{lem: control moment}
    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
\begin{itemize}
\item[(1)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$;
\item[(2)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$;
\item[(3)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
\end{itemize}
\end{lem}
\begin{proof}
    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
    Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
\begin{align}
    &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
        \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
    + |\langle P^\alpha_t g,\mu\rangle|
    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
\end{align}
    By calculating the sum on the right, we get the desired result.
\end{proof}

@@

\subsection{Superprocesses}
\label{sec: definition of superprocess}
    In this subsection, we will give the definition of a general superprocess.
    Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the topology of weak convergence.
    For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$, we use the following convention in this subsection:
\[
    F(x,f):= F(x,f(x)),\quad x\in E.
\]
    A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
\begin{itemize}
\item
    %The spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
    the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
\item
    %The branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
    the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
\begin{equation}
\label{eq: branching mechanism}
    \psi(x,z)=
    -\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
\end{equation}
    where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$;
\item
    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
\begin{equation}
    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
    \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
\end{equation}
    where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq:FKPP_in_definition}
    V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
    = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
    \quad t \geq 0, x \in E.
\end{equation}
\end{itemize}
    We refer our readers to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
    To avoid triviality, we assume that
    $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.

@@

    Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its canonical path denoted by $(W_t)_{t\geq 0}$.
    We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
    Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued},
    there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
\begin{itemize}
\item
    $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
\item
    $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
\item
    %For any $\mu \in \mathcal M(E)$, 
    for any $\mu \in \mathcal M(E)$, 
    if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
    then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
\end{itemize}
    We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
\subsection{{Semigroups for superprocesses}}
\label{sec: definition of vf}
    Let $X$ be a non-persistent superprocess with its Kuznetsov measure denoted by $(\mathbb N_x)_{x\in E}$.
    We define the mean semigroup
\begin{equation}
    P_t^{\rho_1} f(x)
    := \Pi_{x}[e^{\int_0^t \rho_1(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
    \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
\end{equation}
    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
\begin{equation}
\label{eq: mean formula for superprocesses}
   \mathbb N_{\mu}[\langle W_t, f\rangle]
   =\mathbf P_{\mu}[\langle X_t, f\rangle]
   =\mu(P^{\rho_1}_t f).
\end{equation}

@@

\bigskip
\noindent
{\bf Acknowledgment:}
	%We thank Zenghu Li for helpful conversations..
	We thank Zenghu Li and Rui Zhang for helpful conversations.
\bigskip

>>>>

@@

    \\ University of Illinois at Urbana-Champaign

@@

Let $\xi$ be an Ornstein-Uhlenbeck process on $\mathbb R^d$ with generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$, where $\sigma, b >0$. Let $\psi$ be a branching mechanism which is close to a function of the form $\widetilde{\psi}(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$, in some sense. In this paper, we study asymptotic behaviors of
$(\xi, \psi)$-superprocesses $(X_t)_{t\geq 0}$. For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$. Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.

@@

\subsubsection{Critical branching rate regime}
    For each $f\in \mathcal{P}$ satisfying $\alpha\beta=\kappa_f b(1+\beta)$, define
\begin{equation}\label{tilde-m}
    \widetilde{m}[f]
        := \eta\int_{\mathbb R^d} \Big(-i\sum_{p\in \mathbb Z_+^d:|p|=\kappa_f}\langle f,\phi_p\rangle\phi_p(x)\Big)^{1+\beta} \varphi(x)~dx.
\end{equation}
    According to Lemma \ref{lem: def of all m} below, $\widetilde m[f]$ is well-defined.
   We will prove in Lemma \ref{prop: alpha stable rv} that
   $\theta \mapsto \exp( \widetilde m[\theta f])$ is the characteristic function of a $(1+\beta)$-stable random variable.
\begin{thm}
\label{thm: critical clt}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta=\kappa_fb(1+\beta)$, then for any $\mu\in \mathcal M_c(\mathbb R^d)$,
    under $\mathbb{P}_{\mu}(\cdot|D^c)$,
    it holds that
\[
    \frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}
        \xrightarrow[t\to \infty]{d} \widetilde{\zeta},
\]
    where $\widetilde{\zeta}$ is a $(1+\beta)$-stable random variable with
    characteristic function
\[
     \mathbf E [e^{i\theta \widetilde{\zeta}}]
    =\exp(\widetilde{m}[\theta f]),
    \quad \theta\in \mathbb R.
\]
\end{thm}

@@

\begin{proof}
    Fix $h \in \mathcal P$ and $\mu \in \mathcal M_c(\mathbb R^d)$. Let $C_0$ be the constant in the Lemma \ref{lem: temp}.
    For all $\kappa \in \mathbb Z_+$,  $0\leq r\leq s\leq t$ with $s-r \leq 1$,  $g\in \mathcal P$ with $Q_{\kappa} g \leq h$, and $c>0$, we have
\begin{align}
    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|\mathcal I_r^s\langle g, X_t\rangle|>\lambda) d\lambda
    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|\mathcal I_r^s\langle g, X_t\rangle|> \lambda) d\lambda
    \\& \leq c^{1+\gamma} + C_0  e^{\alpha r}(1+\gamma)\int_c^\infty \bigg(\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{1+\beta}+\Big(\frac{e^{(t-s)(\alpha - \kappa b)}}{\lambda}\Big)^{2}\bigg)\lambda^{\gamma}d\lambda
    \\&\leq c^{1+\gamma} e^{\alpha r} + C_0e^{\alpha r}(1+\gamma)\Big(  \frac{e^{(1+\beta)(t-s)(\alpha- \kappa b)}}{(\beta - \gamma)c^{\beta - \gamma}}  + \frac{e^{2(t-s)(\alpha- \kappa b)}}{(1 - \gamma)c^{1 - \gamma}} \Big).
\end{align}
    Taking $c = e^{(t-s)(\alpha- \kappa b)}$, we get
\begin{align}
    &\mathbb P_\mu\big[|\mathcal I_r^s\langle g, X_t\rangle|^{1+\gamma}\big]
    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa b)} e^{\alpha r}\Big(1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}\Big).
\end{align}
    Note that
\begin{align}
    &(1+\beta)(t-s)(\alpha- \kappa b) + \alpha r
    = (t-s)\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b)
    \\&\leq t\alpha+(t-s) (\beta\alpha- (1+\beta)\kappa b).
\end{align}
    So the desired result is true with
\[
    C
    := 1+ C_0 \frac{1+\gamma}{\beta - \gamma}+ C_0 \frac{1+\gamma}{1 - \gamma}.
    \qedhere
\]
\end{proof}
    For each random variable $\{Y; \mathbb P\}$ and $p \in [1,\infty)$, we write
\[
    \|Y\|_{\mathbb P;p}:= \mathbb P[|Y|^p]^{1/p}.
\]
\begin{lem}
\label{lem: control moment}
    For all $h \in \mathcal P$, $\mu \in \mathcal M_c(\mathbb R^d)$, $\gamma\in (0, \beta)$ and $\kappa \in \mathbb Z_+$, there exists a constant $C > 0$ such that for each $t\geq 0$, we have
\begin{itemize}
\item[(1)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa b)t}$ provided $\alpha\gamma > \kappa (1+\gamma)b$;
\item[(2)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h}\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa (1+\gamma)b$;
\item[(3)]
    $\sup_{g\in \mathcal P: Q_\kappa g \leq h} \|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa (1+\gamma)b$.
\end{itemize}
\end{lem}
\begin{proof}
    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$.
    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
    Using the triangle inequality, for all $\kappa\in \mathbb Z_+$, $g \in \mathcal P$ with $Q_\kappa g \leq h$ and $t\geq 0$, we have
\begin{align}
    &\|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
        \\ &\leq \sum_{l=0}^{\lfloor t\rfloor - 1}\big\| \mathcal{I}_{t-l-1}^{t-l}\langle g,X_t\rangle \big\|_{\mathbb P_\mu;1+\gamma}+\big\| \mathcal{I}_{0}^{t-\lfloor t \rfloor}\langle g,X_t\rangle  \big\|_{\mathbb P_\mu;1+\gamma}
    + |\langle P^\alpha_t g,\mu\rangle|
    \\ &\leq C^{\frac{1}{1+\gamma}} e^{\frac{\alpha}{1+\gamma}t} \sum_{l=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa (1+\gamma)b}{1+\gamma} l} + e^{(\alpha - \kappa b)t} \langle h,\mu\rangle.
\end{align}
    By calculating the sum on the right, we get the desired result.
\end{proof}

@@

\subsection{Superprocesses}
\label{sec: definition of superprocess}
    In this subsection, we will give the definition of a general superprocess.
    Let $E$ be locally compact separable metric space. Denote by $\mathcal M(E)$ the collection of all the finite measures on $E$ equipped with the topology of weak convergence.
    For each function $F(x,z)$ on $E\times \mathbb R_+$ and each $\mathbb R_+$-valued function $f$ on $E$, we use the following convention in this subsection:
\[
    F(x,f):= F(x,f(x)),\quad x\in E.
\]
    A process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is said to be a $(\xi,\psi)$-superprocess if
\begin{itemize}
\item
    the spatial motion $\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ is an $E$-valued Hunt process with its lifetime denoted by $\zeta$;
\item
    the branching mechanism $\psi: E\times[0,\infty) \to \mathbb R$ is given by
\begin{equation}
\label{eq: branching mechanism}
    \psi(x,z)=
    -\rho_1(x) z + \rho_2 (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy).
\end{equation}
    where $\rho_1 \in \mathcal B_b(E)$, $\rho_2 \in \mathcal B_b(E, \mathbb R_+)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$;
\item
    $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M(E)}\}$ is an $\mathcal M(E)$-valued Hunt process with transition probability determined by
\begin{equation}
    \mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
    \quad t\geq 0, \mu \in \mathcal M(E), f\in \mathcal B^+_b(E),
\end{equation}
    where for each $f\in \mathcal B_b(E)$, the function $(t,x)\mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq:FKPP_in_definition}
    V_tf(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi(\xi_s,V_{t-s}f)ds \Big]
    = \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
    \quad t \geq 0, x \in E.
\end{equation}
\end{itemize}
    We refer our readers to \cite{Li2011Measure-valued} for more discussions about the definition and the existence of superprocesses.
    To avoid triviality, we assume that
    $\psi(x,z)$ is not identically equal to $-\rho_1(x)z$.

@@

    Denote by $\mathbb W$ the space of $\mathcal M(E)$-valued c\`{a}dl\`{a}g paths with its canonical path denoted by $(W_t)_{t\geq 0}$.
    We say $X$ is \emph{non-persistent} if $\mathbf P_{\delta_x}(\|X_t\|= 0) > 0$ for all $x\in E$ and $t> 0$.
    Suppose that $(X_t)_{t\geq 0}$ is non-persistent, then according to \cite[Section 8.4]{Li2011Measure-valued},
    there is a unique family of measures $(\mathbb N_x)_{x\in E}$ on $\mathbb W$ such that
\begin{itemize}
\item
    $\mathbb N_x (\forall t > 0, \|W_t\|=0) =0$;
\item
    $\mathbb N_x(\|W_0 \|\neq 0) = 0$;
\item
    for any $\mu \in \mathcal M(E)$, 
    if $\mathcal N$ is a Poisson random measure defined on some probability space with intensity $\mathbb N_\mu(\cdot):= \int_E \mathbb N_x(\cdot )\mu(dx)$,
    then the superprocess $\{X;\mathbf P_\mu\}$ can be realized by $\widetilde X_0 := \mu$ and $\widetilde X_t(\cdot) := \mathcal N[W_t(\cdot)]$ for each $t>0$.
\end{itemize}
    We refer to $(\mathbb N_x)_{x\in E}$ as the \emph{Kuznetsov measures} of $X$.
\subsection{{Semigroups for superprocesses}}
\label{sec: definition of vf}
    Let $X$ be a non-persistent superprocess with its Kuznetsov measure denoted by $(\mathbb N_x)_{x\in E}$.
    We define the mean semigroup
\begin{equation}
    P_t^{\rho_1} f(x)
    := \Pi_{x}[e^{\int_0^t \rho_1(\xi_s)ds}f(\xi_t) \mathbf 1_{t< \zeta}],
    \quad t\geq 0, x\in E, f\in \mathcal B_b(E,\mathbb R_+).
\end{equation}
    It is known from \cite[Proposition 2.27]{Li2011Measure-valued} and \cite[Theorem 2.7]{Kyprianou2014Fluctuations} that for all $t > 0$, $\mu \in \mathcal M(E)$ and $f\in \mathcal B_b(E,\mathbb R_+)$,
\begin{equation}
\label{eq: mean formula for superprocesses}
   \mathbb N_{\mu}[\langle W_t, f\rangle]
   =\mathbf P_{\mu}[\langle X_t, f\rangle]
   =\mu(P^{\rho_1}_t f).
\end{equation}

@@

\bigskip
\noindent
{\bf Acknowledgment:}
	We thank Zenghu Li and Rui Zhang for helpful conversations.
\bigskip
